### 2012-07-13 joint action and knowing others minds/interacting mindreaders.3.ps.corrections.tex
changes to minimal theor yof mind requested after accept --- include papa on Jonathan Bennett acknolwedge

%\def \papersize {a4paper}
\def \papersize {letterpaper}
\documentclass[12pt,\papersize]{extarticle}
% extarticle is like article but can handle 8pt, 9pt, 10pt, 11pt, 12pt, 14pt, 17pt, and 20pt text

@@

\input{preamble_steve_paper2}
%\author{}

@@

Note that our actions could have a distributive goal even without us each intending that we do something.
As another variation on the turnip-pulling story,
suppose that we each individually intend to 
	contribute to pulling up the turnip or pull it up.
Such intentions are agent neutral in this sense:
relative to such an intention an agent 
	could succeed by acting alone 
and
  she also could succeed by acting with unspecified other agents.
Plausibly our having these intentions is sufficient for our actions to have a distributive goal.
For in virtue of these intentions each of our actions is directed to the turnip's extraction,
and this is an outcome relative to which it is possible that all of our actions succeed.

@@

As well as having true beliefs concerning the goal of your actions, the other must be willing to pursue this goal. 
This is not guaranteed by the truth of the premises of the inference. 
For all these require, the other might be aware of the goal you envisage but attempting to initiate a joint action directed to another, quite different goal%
%and would be unwilling to perform actions directed to the goal you envisage, so that the conclusion of the inference is false
.  
Perhaps, for example, the other disapproves of your project and is offering to act with you as part of an attempt to divert you.\footnote{
We are grateful to anonymous referee for emphasising this point.
}
Note, however, that it is only reasonable for the other to attempt a joint action with you where you are in a position to know which goal the joint action would be directed to. 
If no alternative goal ought to be salient to you and the other has done nothing to make an alternative salient, then it is not unreasonable for you to ignore the possibility that the other is unwilling to pursue the goal to which your actions will be directed. 
This might easily be the case where, for instance, you are in a tidy kitchen patiently chopping your way through a large pile of carrots; it is perhaps less likely to be the case in a more cluttered kitchen where you are surrounded by all kinds of potential ingredient in different states of preparation. 
In general, how strongly the truth of the premises of the your-goal-is-my-goal inference supports the truth of the conclusion will depend (among other conditions) on how salient alternative goals to which your actions might be directed ought to be to you.

@@

As this example indicates,
exploiting your-goal-is-my-goal 
can shift the burden of identifying goals from a mindreader to her target.
In the example Ayesha is the focal mindreader and we are her target;
but her success in identifying the goal of our actions
depends on this,
that our willingness to act jointly with her is based on \emph{our} knowledge of the goals of \emph{her} actions.
In purely observational mindreading, the target's beliefs about the goals of the mindreader's actions are not normally relevant (except, of course, when the mindreader is ascribing such beliefs).
But interacting mindreaders who rely on your-goal-is-my-goal
thereby rely on their targets' having correctly identified the goals of their actions.
Of course this is sometimes a reason not to rely on your-goal-is-my-goal.
But where the target understands relevant means-ends relations,
such as actions involving novel tools,
the your-goal-is-my-goal route to knowledge of others' goals may sometimes be the only option.

@@

\end{enumerate}
%
Therefore:
%
\begin{enumerate}[resume]
%
\item A goal of her actions will be his goal, the goal to which his actions will be directed.
\end{enumerate}
%
Call this inference \emph{her-goal-is-his-goal}.  
This inference shows that mere observers who understand interaction also have a route to knowledge of other's goals that avoids the problem of opaque means. 
The significance of interaction for mindreading extends beyond cases in which the mindreader herself interacts.

@@

\bibliography{phd_biblio}

>>>>

\def \papersize {a4paper}
%\def \papersize {letterpaper}
\documentclass[12pt,\papersize]{extarticle}
% extarticle is like article but can handle 8pt, 9pt, 10pt, 11pt, 12pt, 14pt, 17pt, and 20pt text

@@

\input{$HOME/Documents/submissions/preamble_steve_paper2}
%\author{}

@@

Note that our actions could have a distributive goal even without us each intending that we do something.
As another variation on the turnip-pulling story,
suppose that we each individually intend to 
	contribute to pulling up the turnip or pull it up.
Such intentions are agent-neutral in this sense:
relative to such an intention an agent 
	could succeed by acting alone 
and
  she also could succeed by acting with unspecified other agents.
Plausibly our having these intentions is sufficient for our actions to have a distributive goal.
For in virtue of these intentions each of our actions is directed to the turnip's extraction,
and this is an outcome relative to which it is possible that all of our actions succeed.

@@

As well as having true beliefs concerning the goal of your actions, the other must be willing to pursue this goal. 
This is not guaranteed by the truth of the premises of the inference. 
For all these require, the other might be aware of the goal you envisage but attempting to initiate a joint action directed to another, quite different goal%
%and would be unwilling to perform actions directed to the goal you envisage, so that the conclusion of the inference is false
.  
Perhaps, for example, the other disapproves of your project and is offering to act with you as part of an attempt to divert you.\footnote{
We are grateful to anonymous referee for emphasising this point.
}
Note, however, that it is only reasonable for the other to attempt a joint action with you where you are in a position to know which goal the joint action would be directed to. 
If no alternative goal ought to be salient to you and the other has done nothing to make an alternative salient, then it is not unreasonable for you to ignore the possibility that the other is unwilling to pursue the goal to which your actions will be directed. 
This might easily be the case where, for instance, you are in a tidy kitchen patiently chopping your way through a large pile of carrots; it is perhaps less likely to be the case in a more cluttered kitchen where you are surrounded by all kinds of potential ingredients in different states of preparation. 
In general, how strongly the truth of the premises of the your-goal-is-my-goal inference supports the truth of the conclusion will depend (among other conditions) on how salient alternative goals to which your actions might be directed ought to be to you.

@@

As this example indicates,
exploiting your-goal-is-my-goal 
can shift the burden of identifying goals from a mindreader to her target.
In the example Ayesha is the focal mindreader and we are her target;
but her success in identifying the goal of our actions
depends on this,
that our willingness to act jointly with her is based on \emph{our} knowledge of the goals of \emph{her} actions.
In purely observational mindreading, the target's beliefs about the goals of the mindreader's actions are not normally relevant (except, of course, when the mindreader is ascribing such beliefs).
But interacting mindreaders who rely on your-goal-is-my-goal
thereby rely on their targets having correctly identified the goals of their actions.
Of course this is sometimes a reason not to rely on your-goal-is-my-goal.
But where the target understands relevant means-ends relations,
such as actions involving novel tools,
the your-goal-is-my-goal route to knowledge of others' goals may sometimes be the only option.

@@

\end{enumerate}
%
Therefore:
%
\begin{enumerate}[resume]
%
\item A goal of her actions will be his goal, the goal to which his actions will be directed.
\end{enumerate}
%
Call this inference \emph{her-goal-is-his-goal}.  
This inference shows that mere observers who understand interaction also have a route to knowledge of others' goals that avoids the problem of opaque means. 
The significance of interaction for mindreading extends beyond cases in which the mindreader herself interacts.

@@

\bibliography{$HOME/endnote/phd_biblio}

### 2012-07-13 mindreading/minimal theory of mind (new version)/minimal theory of mind.nv.tex
changes to minimal theor yof mind requested after accept --- include papa on Jonathan Bennett acknolwedge

\def \ititle {How to Construct a Minimal Theory of Mind}
\def \isubtitle {}
\def \iauthor {Stephen A. Butterfill \& Ian A. Apperly}
\def \iemail{s.butterfill@warwick.ac.uk}
%for anonymous submisison
\def \iauthor {}
\def \iemail{}
%\date{}

@@

%these two lines are for anonymous submission --- they remove author and date
%but don't forget to remove defs above as well --- otherwise it will be in the metadata
\author{}
\date{}

@@

@@

Given this analysis, it is notable that one study already claims to have found positive evidence that infants can ascribe beliefs about identity. 
Scott and Baillargeon (\citeyear{en_1690}) have already conducted experiments which aim to show that 18-month-old infants are able to represent beliefs involving mistakes about `which particular object \textit{token}' another is facing rather than only about `which \textit{type} of object' is present (p.\ 1179). However, while their aim is clearly relevant, we shall show that these experiments do not succeed in testing whether infants ascribe beliefs about identity.  In essence, their paradigm involves two types of object, a divisible penguin which affords hiding a key and an indivisible penguin which lacks this affordance.  The divisible penguin has two states, divided and whole.  When whole it is visually indistinguishable from the indivisible penguin which does not afford hiding a key.  Infants sit opposite a protagonist.  Familiarisation trials provide information that the protagonist can expect there to be two penguins in the scene at all times, one of each type; these trials also provide information that the protagonist can expect the divisible penguin to appear in its divided state. In the critical condition, the scene contains an uncovered and a covered penguin. The uncovered penguin is divisible but, because it is in the whole state, it might easily be taken to be indivisible.  The covered penguin is indivisible.  The findings suggest that infants know that the uncovered penguin is divisible but expect the protagonist to believe that the uncovered penguin is indivisible and to infer that the covered penguin is divisible.  Does this pattern of knowledge and expectation require that the infants have attributed a false belief about identity?  This is not necessary. Suppose that infants attributed the following reasoning to the protagonist: this penguin visible on my right is \textit{an} indivisible penguin; \textit{a} divisible penguin is always present; therefore there is \textit{a} divisible penguin under the cover.  This reasoning concerns only the types of objects present and does not involve identity. Yet it is sufficient (together with some further inferences about the protagonists’ goal) for success. So while Scott and Baillargeon’s (2010) findings are interesting in many respects, their implementation does not provide evidence that infants ascribe beliefs about identity.

@@

For other subjects we need an indirect measure.  If subjects sometimes represent encounters or perceptions as such, then representations of others’ encounters may interfere with expectations or judgements about reality or with judgements about one’s own perceptions and beliefs \citep[so-called `altercentric interference',][]{Samson:2010jm}.  For example, representing a protagonists’ encounter with an object at a particular location may interfere with expectations about the object’s actual location.  Accordingly, evidence that there is such interference when in a situation where others have different perceptions or beliefs would provide indirect evidence for theory of mind cognition (minimal or full-blown) over behavioural strategies, for such interference would be difficult to explain if subjects were representing behaviours only. Evidence showing this kind of altercentric interference has recently been found in human adults \citep[]{en_1797, Samson:2010jm}. These studies show that adults’ judgements about the number of objects they could see in a visual scene were slower and more error-prone when the scene contained an irrelevant other whose perspective was different, suggesting that another’s perspective can cause altercentric interfere.

>>>>

\def \ititle {How to Construct a Minimal Theory of Mind}
\def \isubtitle {}
\def \iauthor {Stephen A. Butterfill \& Ian A. Apperly}
\def \iemail{s.butterfill@warwick.ac.uk}
%for anonymous submisison
%\def \iauthor {}
%\def \iemail{}
%\date{}

@@

%these two lines are for anonymous submission --- they remove author and date
%but don't forget to remove defs above as well --- otherwise it will be in the metadata
%\author{}
%\date{}

@@

Our approach is inspired by a tradition of creature construction in philosophy, and in particular by Bennett’s construction in \textit{Linguistic Behaviour} (\citeyear{Bennett:1976rg}).  Of course, where Bennett and others aimed to understand something about what it is for a subject to have desires, beliefs and other mental states, our main aim is to understand what might be involved in tracking and thinking about these things.

@@

Given this analysis, it is notable that one study already claims to have found positive evidence that infants can ascribe beliefs about identity. 
Scott and Baillargeon (\citeyear{en_1690}) have already conducted experiments which aim to show that 18-month-old infants are able to represent beliefs involving mistakes about `which particular object \textit{token}' another is facing rather than only about `which \textit{type} of object' is present (p.\ 1179). However, while their aim is clearly relevant, we shall show that these experiments do not succeed in testing whether infants ascribe beliefs about identity.  In essence, their paradigm involves two types of object, a divisible penguin which affords hiding a key and an indivisible penguin which lacks this affordance.  The divisible penguin has two states, divided and whole.  When whole it is visually indistinguishable from the indivisible penguin which does not afford hiding a key.  Infants sit opposite a protagonist.  Familiarisation trials provide information that the protagonist can expect there to be two penguins in the scene at all times, one of each type; these trials also provide information that the protagonist can expect the divisible penguin to appear in its divided state. In the critical condition, the scene contains an uncovered and a covered penguin. The uncovered penguin is divisible but, because it is in the whole state, it might easily be taken to be indivisible.  The covered penguin is indivisible.  The findings suggest that infants know that the uncovered penguin is divisible but expect the protagonist to believe that the uncovered penguin is indivisible and to infer that the covered penguin is divisible.  Does this pattern of knowledge and expectation require that the infants have attributed a false belief about identity?  This is not necessary. Suppose that infants attributed the following reasoning to the protagonist: this penguin visible on my right is \textit{an} indivisible penguin; \textit{a} divisible penguin is always present; therefore there is \textit{a} divisible penguin under the cover.  This reasoning concerns only the types of objects present and does not involve identity. Yet it is sufficient (together with some further inferences about the protagonist’s goal) for success. So while Scott and Baillargeon’s (2010) findings are interesting in many respects, their implementation does not provide evidence that infants ascribe beliefs about identity.

@@

For other subjects we need an indirect measure.  If subjects sometimes represent encounters or perceptions as such, then representations of others’ encounters may interfere with expectations or judgements about reality or with judgements about one’s own perceptions and beliefs \citep[so-called `altercentric interference',][]{Samson:2010jm}.  For example, representing a protagonist's encounter with an object at a particular location may interfere with expectations about the object’s actual location.  Accordingly, evidence that there is such interference when in a situation where others have different perceptions or beliefs would provide indirect evidence for theory of mind cognition (minimal or full-blown) over behavioural strategies, for such interference would be difficult to explain if subjects were representing behaviours only. Evidence showing this kind of altercentric interference has recently been found in human adults \citep[]{en_1797, Samson:2010jm}. These studies show that adults’ judgements about the number of objects they could see in a visual scene were slower and more error-prone when the scene contained an irrelevant other whose perspective was different, suggesting that another’s perspective can cause altercentric interference.
